Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-04-21 paper/ms.tex
Cite Regan and Teuben
Bold cosmo sims section

\subsection{Previous Simulation Work}
{\bf Substantial work has been devoted to the role of gas in bar dynamics. We
discuss this and highlight the novel aspects of the present investigation.}

@@

{\bf There may also be issues related to structural differences between their
bars and the bar considered in this work. In our case, we allowed the bar to
form in an $N$-body run and then added gas after the bar formation. In
\citet{2013MNRAS.429.1949A, 2014MNRAS.438L..81A} the bar forms from a disk that
is initially gas-rich. Neither approach is inherently better, but it is known
that in the latter case the resultant bar strength is weaker for initially
gas-rich systems \citep[e.g.,][]{2013MNRAS.429.1949A}. Weaker bars should be
less efficient at driving gas inwards and thus experience less positive torque
from the gas phase. A direct comparison based on the torque by the gas phase on
the bar is necessary.}

@@

\subsection{Cosmological Simulations}
Barred galaxies in cosmological simulations of galaxy formation continue to be
in conflict with observations by producing bars which rotate too slowly
\citep{2017MNRAS.469.1054A, 2019MNRAS.483.2721P, 2021AA...650L..16F,
2022ApJ...940...61F}.\footnote{Though see \citet{2022ApJ...940...61F} who argue
bars have consistent pattern speeds with observations, but are too short.}
\citet{2015PASJ...67...63O} describe cosmological zoom simulations of two barred
Milky Way-like galaxies that both slow down over time. As pointed out by
\citet{2010ApJ...719.1470V}, the gas fraction cutoff for the stable pattern
speed regime increases with lower softening lengths. \citet{2015PASJ...67...63O}
use softening lengths larger than ours by about a factor of $6$. This highlights
the importance of future work exploring precisely when barred galaxies ought to
be in the stable regime.

>>>>

\subsection{Previous Idealized Simulation Work}
{\bf Substantial work has been devoted to the role of gas in bar dynamics. We
discuss this and highlight the novel aspects of the present investigation.}

@@

{\bf There may also be issues related to structural differences between their
bars and the bar considered in this work. In our case, we allowed the bar to
form in an $N$-body run and then added gas after the bar formation. In
\citet{2013MNRAS.429.1949A, 2014MNRAS.438L..81A} the bar forms from a disk that
is initially gas-rich. Neither approach is inherently better, but it is known
that in the latter case the resultant bar strength is weaker for initially
gas-rich systems \citep[e.g.,][]{2013MNRAS.429.1949A}. Weaker bars are less
efficient at driving gas inwards \citep{2004ApJ...600..595R} and thus should
experience less positive torque from the gas phase. A direct comparison based on
the torque by the gas phase on the bar is necessary.}

@@

\subsection{Cosmological Simulations}
Barred galaxies in cosmological simulations of galaxy formation continue to be
in conflict with observations by producing bars which rotate too slowly
\citep{2017MNRAS.469.1054A, 2019MNRAS.483.2721P, 2021AA...650L..16F,
2022ApJ...940...61F}.\footnote{Though see \citet{2022ApJ...940...61F} who argue
bars have consistent pattern speeds with observations, but are too short.}
{\bf \citet{2015PASJ...67...63O} describe cosmological zoom simulations of two barred
Milky Way-like galaxies that both slow down over time. As pointed out by
\citet{2010ApJ...719.1470V}, the gas fraction cutoff for the stable pattern
speed regime increases with lower softening lengths. \citet{2015PASJ...67...63O}
use softening lengths larger than ours by about a factor of $6$. This highlights
the importance of future work exploring precisely when barred galaxies ought to
be in the stable regime.}

{\bf \citet{2021AA...650L..16F} explored the evolution of bars in the Auriga
cosmological zoom simulations \citep{2017MNRAS.467..179G}. They find \Rot{}
values consistent with observations. Furthermore, their pattern speed evolution
shows some apparent periods of stability (see their Fig.~B1). One galaxy, Au27,
appears to even transition from the stable pattern speed regime to the slowing
down regime at a lookback time of $\sim1.8\,\textrm{Gyr}$.}
